### 2018-10-17 Latex/section_methods.tex
mainly typos

equations in a quadratic domain with periodic boundary conditions using a
standard pseudo spectral code. The simulations were started from zero initial

@@

by the number of nodes, $n$, in the each direction and has been varied from 960

@@

domain. The forcing is white noice in time and designed so that the energy

@@

The time evolution of mean energy is shown in figure~\ref{fig_Evstime} for all
twenty simulations. After an initial period of growth, mean energy is leveling
out at different values for different runs. This is not the same picture as we
see in simulations of three-dimensional incompressible turbulence or stratified
turbulence, where all curves would have leveled out more or less at the same
value. We find that mean energy in the stationary state is a function of both $
c $ (or the Froude number) and resolution $ n $ and that the functional
dependence can be approximately written as
\begin{equation} \label{MeanEnergy}
E \propto \sqrt{L_f c \eps} \, n^{\alpha}  \, ,
\end{equation}
where $ L_f = \pi/k_f $ is the forcing scale. In figure \ref{MeanE} to the
left, we see $ E/\sqrt{\eps} $ as function of $ c $ for different resolutions $
n $. For each resolution the points are approaching a power law $ C_n c^{1/2} $
with increasing values of $ C_n $ for increasing $ n $. In the same figure to
the right we see $ E/\sqrt{L_f c \eps} $ for different values of $ c $. For
each $ c $ the points follow a power law $ n^{\alpha} $, where $ \alpha $ is
becoming slightly larger with increasing $ c $, approaching almost the same
value $ \alpha \approx 0.33 $ for the three highest values of $ c $. The
relation (\ref{MeanEnergy}) can be reformulated as
\begin{equation} \label{Dissipation}
\frac{\eps} {(E^{3/2} / L_f)} \propto \frac{E^{1/2}}{c} n^{-2\alpha}
\end{equation}
Since the simulations are well resolved the dependence on resolution should not
be interpreted as consequence of the numerics but rather as a Reynolds number
effect, although it is not hundred percent clear how a Reynolds number should
be defined in our case. We may note, however, that $ n $ is proportional $
k_{d} / k_f $ and the corresponding ratio in Kolmogorov turbulence scales as $
Re^{3/4} $ since the Kolmogorov scale is proportional to $ \nu^{3/4} $, where $
\nu $ is the kinematic viscosity. If we simply define a Reynolds number as
\begin{equation}
Re = \left ( \frac{k_d} {k_f} \right )^{4/3} \, ,
\end{equation}
we can substitute $ n^{-2\alpha} $ in (\ref{Dissipation}) with $ Re^{-8
\alpha/3} $. The normalised energy dissipation on the left hand side of
(\ref{Dissipation}) will thus go to zero in the limit of large Reynolds number.
This is very different from three-dimensional turbulence where there is a local
Richardson-Kolmogorov cascade, in which energy is successively transfered from
large to small scales of motion. That the cascade is local means that eddies of
a particular scale are not directly influenced by eddies of widely different
scales. As a consequence, the normalized dissipation is of the order of unity
independent of Reynolds number \cite[]{Pope, TennekesLumley}. A review of the
experimental evidence and theoretical implications of this fundamental law of
Kolmogorov turbulence is given by \cite{Vassilicos2015}. Our result
(\ref{Dissipation}) suggests that SW wave turbulence does not fit into the
paradigm of a local Richardson-Kolmogorov cascade. Moreover, it is not only in
the limit of large Reynolds number the normalized dissipation will go to zero
but also in the limit of strong stratification, $ E^{1/2}/c \rightarrow 0 $.
This is different from three-dimensional stratified turbulence where the ratio
on the left hand side of (\ref{Dissipation}) is of the order of unity in the
limit of strong stratification \cite[]{Lindborg2006, Brethouwer2007}.

The `four-fifths law' for the third order structure function of Kolmogorov
turbulence is often derived using the assumption of a local cascade
\cite[]{Vassilicos2015} or the assumption that dissipation stays finite in the
limit of large Reynolds number \cite[]{Frisch}. As we just discussed, these
assumptions seem to be violated in the case of SW wave turbulence.
Nevertheless, the analogous law (\ref{eq_Kolmo}) that we derived for SW wave
turbulence is satisfied with a high degree of accuracy in our simulations. In
figure \ref{Flux} we wee the spectral energy flux from run W7 to the left and
the third order structure function to the right. There is a broad constant flux
range with equipartition between KE and APE flux and an almost equally broad
range where (\ref{eq_Kolmo}) is satisfied, with equipartition between the two
third order structure functions associated with KE and APE. The assumptions of
a local cascade and finite dissipation do not seem to be necessary in order for
the third order structure function law (\ref{eq_Kolmo}) to be valid.

@@

Visualizations of the flow field give a completely different picture from what
may be expected from a collection of linear gravity waves. They are totally
dominated by the appearance of shock waves. In figure (\ref{Physical}) we see
the divergence, $ \nabla \cdot {\bf u} $, to the left and the velocity
component in the $ y $-direction, $ u_y $, to the right. The two figures at the
top are from run W6 while the two figures at the bottom are from run W17. The
difference between the two runs is that $ c $ is larger by a factor of $ 20 $
in W17 as compared to W6. To the left we see the shocks displayed as elongated
bands of negative divergence. That the divergence is negative at the shocks can
be understood from the fact that the velocity component perpendicular to the
shock always has a negative jump in the direction of shock propagation.
Apparently, the mean distance between the shocks is considerably smaller in run
W17 with the larger value of $ c $ compared to run $ W6 $ with the smaller
value of $ c $. The shocks are also visible in the figures to right where $ u_y
$ is displayed. It may be interesting to note that the shocks along the $ x
$-axis appear as extra sharp in this plot, since there is a strong jump of $
u_{y} $ over these shocks, while the shocks along the $ y $-axis are hardly
visible, since there is no jump of $ u_{y} $ over these. In the two figures to
the right we see a variation of the flow field over the length scale $ L_f $
which is not seen in the two figures to the left. This variation is evidently a
footprint of the random forcing. Although the forcing length scale $ L_f $ is
the same in the two simulations the mean distance, $ d $, between the shocks is
much smaller in run $ W17 $ than in run $ W6 $, which may seem a little bit
surprising. We have calculated $ d $ by counting the number of negative spikes
of the divergence along ten lines parallel to the $ x $-axis and ten lines
parallel to the $ y $-axis and then divided total length of all the lines by
the number of spikes. Generally, we found that $ d \sim c^{-1/2} $, or
\begin{equation} \label{MeanDistance}
d \propto L_f F_f ^{1/2} \, ,
\end{equation}
independent of resolution $ n $. In figure (\ref{fig_distance}) we have plotted
$ d/L_f $ versus Froude number for all twenty runs. As can be seen the points
follow the $ F_f^{1/2} $-curve quite well, although there seems to be a slight
systematic deviation at the highest $ F_f $, which may be due to the fact that
$ d $ is rather close to the length of the side of the box for the largest $
F_f $.

@@

We will now present the results for the structure functions. Substituting
(\ref{MeanDistance}) into (\ref{StrucFunc}) we find that the structure
functions are expected to scale as
\begin{equation} \label{StrucFunc2}
\meane{|\delta u |^p}  \sim \meane{(c|\delta h |)^p} \sim  (L_f F_f^{1/2})^{p/3-1}  \eps^{p/3}  r  \, .
\end{equation}
for separation distances that fulfill the condition $ \delta x \ll r \ll d $,
where $ \delta x $ is the shock width. The scaling (\ref{StrucFunc2}) is
expected to become better and better fulfilled with decreasing $ c $ (or
increasing $ F_f $), for two reasons. First, according to (\ref{MeanDistance})
$ d $ is increasing with $ F_f $, and the scaling range is therefore becoming
wider for decreasing $ c $, if $ \delta x $ or the resolution $ n $ is kept
constant. Second, according to (\ref{Strength}) the amplitude of the shocks
scales as $ (\eps d)^{1/3} $, which means that the shocks are becoming
increasingly strong for large $ d $ (small $ c $). Thus, the assumption that
the structure functions are totally dominated by increments where a shock is
crossed will be better fulfilled for small $ c $. This effect is expected to be
particularly important for lower order structure functions. The scaling
(\ref{StrucFunc2}) is also expected top become better and better fulfilled with
increased resolution $ n $, since $ \delta x $ is decreasing with increasing $
n $.

As expected, we have found that the displacement structure functions scale
exactly in the same way as the velocity structure functions, why we only plot
velocity structure functions. In figure (\ref{fig_StrucFunc}) we see the
compensated and normalised second, fourth and sixth order longitudinal
structure functions from the five simulations with $ n = 3840 $ to the left and
the three simulations with $ n = 7860 $ to the right. At small separation, $ r
< \delta x $, the structure functions have the dependence $ \sim r^{p} $, which
is characteristic of a smooth velocity field, indicating that the shocks are
reasonably well resolved. There is a small bump around the shock width, $ r
\approx \delta x $, and at $ r > \delta x $, there is a range where the
compensated structure functions are flat, or almost flat. As expected, this
range is becoming broader for smaller $ c $ (or larger $ F_f $). The range is
also broader in the higher resolution runs to the right as compared to the
lower resolution simulations to the left. There is clearly a better collapse of
the curves for the sixth order structure functions compared to the second order
structure functions. This is not surprising, since the shock contribution to
the structure functions should become increasingly dominant with increasing
order. Plots of the transverse structure functions are very similar to the
plots of the longitudinal structure functions, with the difference that the
transverse structure functions are somewhat smoother at $ r \approx \delta x $.
In figure (\ref{fig_ratio}) we see the ratio $ R_{p}(r) = \langle \mid \delta
u_L \mid ^{p} \rangle / \langle \mid \delta u_T \mid ^{p} \rangle$ for $ p=
2,3,4,5,6 $ from run W4, together with dotted straight lines, indicating the
values predicted by (\ref{Ratio}). As can be seen, there is a quite good
agreement with the predicted values in a limited range of separations, $ r >
\delta x $. Somewhat unexpectedly, the range in which there is a good agreement
becomes more narrow with increasing $ p $, an observation that we cannot
explain. It may also be noted that $ R_2 \rightarrow 3 $ in the limit of small
$ r $, which is the theoretical single point limit for an irrotational
isotropic field. In figure (\ref{fig_flatness}) we se the flatness factor, $
F_T $, of the transverse structure functions at the top and the ratio, $
F_T/F_L $, at the bottom. The figures to the left show the results from the
five simulations with $ n = 3840 $ and the figures to the right show the
results from the three simulations with $ n = 7860 $. The flatness factor shows
increasingly large values for decreasing $ r $ with a dependence that is rather
close to but somewhat steeper than $ r^{-1} $. At small $ r $ the curves are
leveling out at very large values. For $ n = 7869 $ and $ c = 10 $ we see that
$ F_{T} \approx 400 $ at small $ r $. The degree to which the flatness factor
is increasing with decreasing scale is by some authors defined as the most
appropriate measure of spatial intermittency \cite[see for example][]{Frisch}.
If this measure is used, SW wave turbulence is, indeed, extremely intermittent.
In the two figures at the bottom we see that $ F_{T}/F_{L} \approx 1.5 $ in a
limited range of separations, $ r > \delta x $, which is becoming somewhat
broader as $ c $ is increasing and is also somewhat broader in the higher
resolution runs shown to the right as compared to the lower resolution runs
shown to the left. This is in accordance with the shock model predictions
(\ref{FL}) and (\ref{FT}).

Finally, we present energy spectra. As expected, we found that APE and KE
spectra were almost indistinguishable from each other, why we only plot the
total spectra. In figure (\ref{fig_spectra_c40}) we see the compensated and
normalised energy spectra from the three highest resolution runs. The
compensated spectra are almost flat in a broad range. In the high wave number
end the compensated spectra show a `bottleneck', which we interpret as a
signature of the shocks, and at the very highest wave numbers the magnitude of
the spectra is strongly decreasing, indicating that the shocks are reasonably
well resolved. The $ k^{-2} $-dependence and the associated scaling predicted
by (\ref{Spectra}) are very well satisfied in a limited range of high wave
numbers close to the bottleneck. At smaller wave number the spectra are
becoming somewhat steeper than $ k^{-2} $ and the spectrum from the run with
largest $ c $ does not collapse perfectly onto the other two spectra.

>>>>

equations in a quadratic domain with periodic boundary conditions using the
standard open-source pseudo-spectral code FluidSim \cite[]{fluiddyn, fluidfft,
fluidsim}.
The simulations were started from zero initial

@@

by the number of nodes, $n$, in each direction and has been varied from 960

@@

domain. The forcing is white noise in time and designed so that the energy

@@

The time evolution of mean energy is shown in figure~\ref{fig_Evstime} for all
twenty simulations. After an initial period of growth, mean energy is leveling
out at different values for different runs. This is not the same picture as we
see in simulations of three-dimensional incompressible turbulence or stratified
turbulence, where all curves would have leveled out more or less at the same
value. We find that mean energy in the stationary state is a function of both $
c $ (or the Froude number) and resolution $ n $ and that the functional
dependence can be approximately written as
\begin{equation} \label{MeanEnergy}
E \propto \sqrt{L_f c \eps} \, n^{\alpha}  \, ,
\end{equation}
where $ L_f = \pi/k_f $ is the forcing scale. In figure~\ref{MeanE} to the
left, we see $ E/\sqrt{\eps} $ as function of $ c $ for different resolutions $
n $. For each resolution the points are approaching a power law $ C_n c^{1/2} $
with increasing values of $ C_n $ for increasing $ n $. In the same figure to
the right we see $ E/\sqrt{L_f c \eps} $ for different values of $ c $. For
each $ c $ the points follow a power law $ n^{\alpha} $, where $ \alpha $ is
becoming slightly larger with increasing $ c $, approaching almost the same
value $ \alpha \approx 0.33 $ for the three highest values of $ c $. The
relation (\ref{MeanEnergy}) can be reformulated as
\begin{equation} \label{Dissipation}
\frac{\eps} {(E^{3/2} / L_f)} \propto \frac{E^{1/2}}{c} n^{-2\alpha}
\end{equation}
Since the simulations are well resolved the dependence on resolution should not
be interpreted as consequence of the numerics but rather as a Reynolds number
effect, although it is not hundred percent clear how a Reynolds number should
be defined in our case. We may note, however, that $ n $ is proportional $
k_{d} / k_f $ and the corresponding ratio in Kolmogorov turbulence scales as $
Re^{3/4} $ since the Kolmogorov scale is proportional to $ \nu^{3/4} $, where $
\nu $ is the kinematic viscosity. If we simply define a Reynolds number as
\begin{equation}
Re = \left ( \frac{k_d} {k_f} \right )^{4/3} \, ,
\end{equation}
we can substitute $ n^{-2\alpha} $ in (\ref{Dissipation}) with $ Re^{-8
\alpha/3} $. The normalised energy dissipation on the left hand side of
(\ref{Dissipation}) will thus go to zero in the limit of large Reynolds number.
This is very different from three-dimensional turbulence where there is a local
Richardson-Kolmogorov cascade, in which energy is successively transfered from
large to small scales of motion. That the cascade is local means that eddies of
a particular scale are not directly influenced by eddies of widely different
scales. As a consequence, the normalized dissipation is of the order of unity
independent of Reynolds number \cite[]{Pope, TennekesLumley}. A review of the
experimental evidence and theoretical implications of this fundamental law of
Kolmogorov turbulence is given by \cite{Vassilicos2015}. Our result
(\ref{Dissipation}) suggests that SW wave turbulence does not fit into the
paradigm of a local Richardson-Kolmogorov cascade. Moreover, it is not only in
the limit of large Reynolds number the normalized dissipation will go to zero
but also in the limit of strong stratification, $ E^{1/2}/c \rightarrow 0 $.
This is different from three-dimensional stratified turbulence where the ratio
on the left hand side of (\ref{Dissipation}) is of the order of unity in the
limit of strong stratification \cite[]{Lindborg2006, Brethouwer2007}.

The `four-fifths law' for the third order structure function of Kolmogorov
turbulence is often derived using the assumption of a local cascade
\cite[]{Vassilicos2015} or the assumption that dissipation stays finite in the
limit of large Reynolds number \cite[]{Frisch}. As we just discussed, these
assumptions seem to be violated in the case of SW wave turbulence.
Nevertheless, the analogous law (\ref{eq_Kolmo}) that we derived for SW wave
turbulence is satisfied with a high degree of accuracy in our simulations. In
figure~\ref{Flux} we see the spectral energy flux from run W7 to the left and
the third order structure function to the right. There is a broad constant flux
range with equipartition between KE and APE flux and an almost equally broad
range where (\ref{eq_Kolmo}) is satisfied, with equipartition between the two
third order structure functions associated with KE and APE. The assumptions of
a local cascade and finite dissipation do not seem to be necessary in order for
the third order structure function law (\ref{eq_Kolmo}) to be valid.

@@

Visualizations of the flow field give a completely different picture from what
may be expected from a collection of linear gravity waves. They are totally
dominated by the appearance of shock waves. In figure~\ref{Physical} we see
the divergence, $ \nabla \cdot {\bf u} $, to the left and the velocity
component in the $ y $-direction, $ u_y $, to the right. The two figures at the
top are from run W6 while the two figures at the bottom are from run W17. The
difference between the two runs is that $ c $ is larger by a factor of $ 20 $
in W17 as compared to W6. To the left we see the shocks displayed as elongated
bands of negative divergence. That the divergence is negative at the shocks can
be understood from the fact that the velocity component perpendicular to the
shock always has a negative jump in the direction of shock propagation.
Apparently, the mean distance between the shocks is considerably smaller in run
W17 with the larger value of $ c $ compared to run $ W6 $ with the smaller
value of $ c $. The shocks are also visible in the figures to right where $ u_y
$ is displayed. It may be interesting to note that the shocks along the $ x
$-axis appear as extra sharp in this plot, since there is a strong jump of $
u_{y} $ over these shocks, while the shocks along the $ y $-axis are hardly
visible, since there is no jump of $ u_{y} $ over these. In the two figures to
the right we see a variation of the flow field over the length scale $ L_f $
which is not seen in the two figures to the left. This variation is evidently a
footprint of the random forcing. Although the forcing length scale $ L_f $ is
the same in the two simulations the mean distance, $ d $, between the shocks is
much smaller in run $ W17 $ than in run $ W6 $, which may seem a little bit
surprising. We have calculated $ d $ by counting the number of negative spikes
of the divergence along ten lines parallel to the $ x $-axis and ten lines
parallel to the $ y $-axis and then divided total length of all the lines by
the number of spikes. Generally, we found that $ d \sim c^{-1/2} $, or
\begin{equation} \label{MeanDistance}
d \propto L_f F_f ^{1/2} \, ,
\end{equation}
independent of resolution $ n $. In figure~\ref{fig_distance} we have plotted
$ d/L_f $ versus Froude number for all twenty runs. As can be seen the points
follow the $ F_f^{1/2} $-curve quite well, although there seems to be a slight
systematic deviation at the highest $ F_f $, which may be due to the fact that
$ d $ is rather close to the length of the side of the box for the largest $
F_f $.

@@

We will now present the results for the structure functions. Substituting
(\ref{MeanDistance}) into (\ref{StrucFunc}) we find that the structure
functions are expected to scale as
\begin{equation} \label{StrucFunc2}
\meane{|\delta u |^p}  \sim \meane{(c|\delta h |)^p} \sim  (L_f F_f^{1/2})^{p/3-1}  \eps^{p/3}  r  \, .
\end{equation}
for separation distances that fulfill the condition $ \delta x \ll r \ll d $,
where $ \delta x $ is the shock width. The scaling (\ref{StrucFunc2}) is
expected to become better and better fulfilled with decreasing $ c $ (or
increasing $ F_f $), for two reasons. First, according to (\ref{MeanDistance})
$ d $ is increasing with $ F_f $, and the scaling range is therefore becoming
wider for decreasing $ c $, if $ \delta x $ or the resolution $ n $ is kept
constant. Second, according to (\ref{Strength}) the amplitude of the shocks
scales as $ (\eps d)^{1/3} $, which means that the shocks are becoming
increasingly strong for large $ d $ (small $ c $). Thus, the assumption that
the structure functions are totally dominated by increments where a shock is
crossed will be better fulfilled for small $ c $. This effect is expected to be
particularly important for lower order structure functions. The scaling
(\ref{StrucFunc2}) is also expected to become better and better fulfilled with
increased resolution $ n $, since $ \delta x $ is decreasing with increasing $
n $.

As expected, we have found that the displacement structure functions scale
exactly in the same way as the velocity structure functions, why we only plot
velocity structure functions. In figure~\ref{fig_StrucFunc} we see the
compensated and normalised second, fourth and sixth order longitudinal
structure functions from the five simulations with $ n = 3840 $ to the left and
the three simulations with $ n = 7860 $ to the right. At small separation, $ r
< \delta x $, the structure functions have the dependence $ \sim r^{p} $, which
is characteristic of a smooth velocity field, indicating that the shocks are
reasonably well resolved. There is a small bump around the shock width, $ r
\approx \delta x $, and at $ r > \delta x $, there is a range where the
compensated structure functions are flat, or almost flat. As expected, this
range is becoming broader for smaller $ c $ (or larger $ F_f $). The range is
also broader in the higher resolution runs to the right as compared to the
lower resolution simulations to the left. There is clearly a better collapse of
the curves for the sixth order structure functions compared to the second order
structure functions. This is not surprising, since the shock contribution to
the structure functions should become increasingly dominant with increasing
order. Plots of the transverse structure functions are very similar to the
plots of the longitudinal structure functions, with the difference that the
transverse structure functions are somewhat smoother at $ r \approx \delta x $.
In figure~\ref{fig_ratio} we see the ratio $ R_{p}(r) = \langle \mid \delta
u_L \mid ^{p} \rangle / \langle \mid \delta u_T \mid ^{p} \rangle$ for $ p=
2,3,4,5,6 $ from run W4, together with dotted straight lines, indicating the
values predicted by (\ref{Ratio}). As can be seen, there is a quite good
agreement with the predicted values in a limited range of separations, $ r >
\delta x $. Somewhat unexpectedly, the range in which there is a good agreement
becomes more narrow with increasing $ p $, an observation that we cannot
explain. It may also be noted that $ R_2 \rightarrow 3 $ in the limit of small
$ r $, which is the theoretical single point limit for an irrotational
isotropic field. In figure~\ref{fig_flatness} we se the flatness factor, $
F_T $, of the transverse structure functions at the top and the ratio, $
F_T/F_L $, at the bottom. The figures to the left show the results from the
five simulations with $ n = 3840 $ and the figures to the right show the
results from the three simulations with $ n = 7860 $. The flatness factor shows
increasingly large values for decreasing $ r $ with a dependence that is rather
close to but somewhat steeper than $ r^{-1} $. At small $ r $ the curves are
leveling out at very large values. For $ n = 7869 $ and $ c = 10 $ we see that
$ F_{T} \approx 400 $ at small $ r $. The degree to which the flatness factor
is increasing with decreasing scale is by some authors defined as the most
appropriate measure of spatial intermittency \cite[see for example][]{Frisch}.
If this measure is used, SW wave turbulence is, indeed, extremely intermittent.
In the two figures at the bottom we see that $ F_{T}/F_{L} \approx 1.5 $ in a
limited range of separations, $ r > \delta x $, which is becoming somewhat
broader as $ c $ is increasing and is also somewhat broader in the higher
resolution runs shown to the right as compared to the lower resolution runs
shown to the left. This is in accordance with the shock model predictions
(\ref{FL}) and (\ref{FT}).

Finally, we present energy spectra. As expected, we found that APE and KE
spectra were almost indistinguishable from each other, why we only plot the
total spectra. In figure~\ref{fig_spectra_c40} we see the compensated and
normalised energy spectra from the three highest resolution runs. The
compensated spectra are almost flat in a broad range. In the high wave number
end the compensated spectra show a `bottleneck', which we interpret as a
signature of the shocks, and at the very highest wave numbers the magnitude of
the spectra is strongly decreasing, indicating that the shocks are reasonably
well resolved. The $ k^{-2} $-dependence and the associated scaling predicted
by (\ref{Spectra}) are very well satisfied in a limited range of high wave
numbers close to the bottleneck. At smaller wave number the spectra are
becoming somewhat steeper than $ k^{-2} $ and the spectrum from the run with
largest $ c $ does not collapse perfectly onto the other two spectra.
